---
title: Is This Good for the Company?
author: Chris Lundberg
date: '2020-03-02'
slug: is-this-good-for-the-company
Categories:
  - R
Description: ''
Tags:
  - text classification
menu: blog
---

In this post I'm going to build a text classification model using the script from [The Office](https://en.wikipedia.org/wiki/The_Office_(American_TV_series)). I'll use the `R` package `dundermifflin` to access the quote data I'll need to build the classification model as well as various packages from `tidymodels` and the `tidyverse` for data wrangling, data visualization, model fitting and evaluation, and prediction.

First, let's load the packages we'll need and explore the data a bit:

```{r, eval=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
# Load packages and data
library(dundermifflin)
library(tidymodels)
library(tidyverse)
library(textrecipes)
library(ggthemes)

quotes <- office_quotes %>% mutate(character = as_factor(character)) %>% 
  group_by(character) %>% add_tally() %>% filter(n >= 700) %>% 
  select(character, quote, n) 

```

I filtered the data so that we're only going to consider quotes from charters with at least 700 lines, which leaves us with 15 characters. Let's take a look at the data:

```{r, eval=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
# Create bar plot
ggplot(quotes, aes(character)) + geom_bar() +
  coord_flip() + theme_classic() +
  xlab("Character") + ylab("Number of Lines") 

```


